---
pagetitle: THOTH | Contact
---

```{r setup, echo = FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(htmltools)
library(readxl)
```

```{r}
# source("contact_functions.R")
# contact_list <- read_excel("contact_list.xlsx")
# contact_cards <- get_contact_cards(contact_list)
# contact_cards
```

```{r}
div(
  br(),
  img(src = "img/JR.png",
        alt = "Jo\u00E3o Ramalho",
        style = "border-radius: 100%"
        ),
  div(h1("Jo\u00E3o Ramalho"),
        h3("Industrial Data Scientist")
      )
    )
```

João a plus de 20 ans d'expérience dans l'industrie dans nombreuses positions dans la R&D, les opérations et les Systèmes d'Information. Ayant passé successivement par Philip Morris, Rolex et Nestlé, il a une vue exceptionnellement large de la manière dont les produits de consomation sont conçus, industrialisés et fabriqués. Avec un Master en Ingénierie Mechanique du [IST](http://ist.pt/), une certification en gestion de project par [PMI](https://www.pmi.org/) et une certification en Data Science par [DataCamp](https://www.datacamp.com/) il se specialise à présent en Visualisation de Données à l'[EPFL](https://www.extensionschool.ch/).

```{r}
div(
  br(),
  img(src = "img/Selim_ID_3.png",
        alt = "Sélim Ach",
        style = "border-radius: 100%",
        width = "90",
        height = "100"
        ),
  div(h1("Sélim Ach"),
        h3("Economist & Data Scientist")
      )
    )
```

Sélim has more than 15 years of experience acquired in the consumer goods, aviation and consulting services. He held several positions where he was responsible for developing analytical models to transform data into valuable insights. He has a solid understanding of the challenges that many industries are currently facing in the areas of Business Analytics solutions as well as in Data Management and Governance. He holds a Master degree in Econometrics from [TSE](https://www.tse-fr.eu) and a certification in Artificial Intelligence & Business Strategy from [MIT](https://executive.mit.edu). After earning a Data Science certification, he is now specializing in Data Visualization at the Swiss technical university [EPFL](https://www.extensionschool.ch/).

