---
pagetitle: THOTH | DataViz
---

```{r setup, echo = FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(htmltools)
```


```{r}

div(
  br(),
  img(src = "img/dataviz.jpg",
        alt = "",
        style = "border-radius: 100%",
        width = "100",
        height = "100"
        ),
  div(h1("Data Visualization"),
        h3(" ")
      )
    )
```

***
Data visualization and storytelling is changing the way we communicate data insights – for the better. By shaping our facts using the right techniques we can improve understanding and take appropriate actions leading ultimately to effective decisions. 

Data visualization is an important asset for your stakeholders and decision-makers. 

### Combining multiple information in a single graph

##### The case of the mobility index 

This graph indicates the evolution of the mobility index in major European cities based on data collected by "Citymapper".  It allows to understand at a glance how fast citizens are moving in their cities after the lockdown period. 

```{r}

library(readr)
library (janitor)
library(tidyverse)
library(ggthemes)

Citymapper <- read_csv("data/Citymapper.csv",skip = 3) 
   
Citymapper <- Citymapper %>% 
  #clean_names() %>% 
  arrange(Date)

# converting the table
Citymapper_long <- Citymapper %>%
  pivot_longer(!Date,names_to = "City", values_to = "Index")

# select only data after March 2020

Citymapper_long_filter_mar2020 <- Citymapper_long %>% 
  filter(Date >= as.Date("2020-03-01"))

# Select only specific cities

nb_city <- Citymapper_long_filter_mar2020 %>% 
  group_by(City) %>% 
  count()

cities <- c("Lyon","Milan","Hamburg","Brussels", 
            "Berlin","Amsterdam","Madrid",
            "Lisbon","Vienna","Copenhagen","Rome","Paris")

Citymapper_long_filter_mar2020_eu <- Citymapper_long %>% 
  filter(Date >= as.Date("2020-03-01")) %>% 
  filter (City %in% cities)

ggplot(data = Citymapper_long_filter_mar2020_eu,
  mapping = aes(x = Date,y = Index ,group=City,position="dodge")) +
  geom_line(color = "darkblue")+
  facet_wrap(vars(City))+
  geom_smooth(method = "loess",color = "red")+
  labs(title = "Mobility Index in major cities",
       subtitle = "Year 2020",
       x = "Date",
       y = "% of the city moving",
       caption = "Source: Citymapper.com/CMI")+
  theme_economist()+
  ylim(0,1)+
  scale_y_continuous(labels = scales::percent)+
  theme (axis.text.x=element_text(angle=0, hjust=1))+
  theme(axis.text = element_text(size = 10))+   
  theme(plot.title = element_text(size = 20,vjust = 1.5))+
  theme(strip.text = element_text(size=10,vjust = 1))+
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0),vjust = 1.5))

```

